A possible evaluation for the contribution of the presented feedback mechanism is to measure the additional information in the system.
To this end, the FIM, denoted by $\vecnot{J}$, will now be calculated with respect to the DOA $\rBrace{\thetaD}$ and range $\rBrace{\phi}$ parameters. 
As the feedback-based transfer function (\ref{eqn:GeneralFeedbackTransferFunction}) is expressed in frequency domain, we rely on \cite{zeira1990frequency} to express the frequency domain FIM as well. 
\par The $\vBrace{k,l}$'th FIM element, may be expressed as
\begin{equation}\label{eq_FIM_kl_full}
    \resizebox{.9\linewidth}{!}{
        \begin{split}
            J_{k,l}\rBrace{\vEta} 
            =&
            \Re\cBrace{
            \frac{1}{2\pi}
            \int_{-\omega_{s}/2}^{\omega_{s}/2}
            {
            \frac{1}{\Phi\rBrace{\omega}}
            \mathfrak{F}^{*}\left\{
            \frac{\partial z(t)}{\partial\eta_{k}}
            \right\}
            \mathfrak{F}\left\{
            \frac{\partial z(t)}{\partial\eta_{l}}
            \right\}
            d\omega
            }}
            \\ &+
            \frac{T}{4\pi}
            \int_{-\omega_{s}/2}^{\omega_{s}/2}
            \frac{1}{\Phi^{2}\rBrace{\omega}}
            \rBrace{\frac{\partial\Phi\rBrace{\omega}}{\partial\eta_{k}}}^{\ast}
            \frac{\partial\Phi\rBrace{\omega}}{\partial\eta_{l}}
            d\omega
        \end{split}
    }
\end{equation}
where $ \vEta = [\thetaD,\phi]^{T} $ is the parameters vector, $\Re$ stands for the real-part extraction operator, $k,l \in\cBrace{1,2}$, $\Phi\rBrace{\omega}$ is the noise spectrum, $\mathfrak{F}$ is the Fourier transform operator, $T$ is the measurement observation interval and $\omega_{s}$ is the signal bandwidth. 
For simplicity, $\text{n}\rBrace{t}$ is assumed to be a white Gaussian with some constant power spectral density $\Phi(\omega)=\sigma^2$ and independent of the estimated parameters $\vEta$. Hence, the second term in the right-hand-side of \eqref{eq_FIM_kl_full} vanishes. 
Assuming continuously differentiable functions, where order alteration of the Fourier transform and the differentiation operations is allowed, \eqref{eq_FIM_kl_full} simplifies to
\begin{equation}
    \label{eq_beamPatternFreqDomain_FIM}
    % \resizebox{1\linewidth}{!}{
        \begin{split}
            J_{kl}\rBrace{\vEta} = 
            \Re\cBrace{
            \frac{1}{2\pi\sigma^2}
            \int_{-\omega_{s}/2}^{\omega_{s}/2}
            {
            \rBrace{\frac{\partial{}\F{z}\rBrace{\omega}}{\partial\eta_{k}}}^{\ast}
            \frac{\partial{}\F{z}\rBrace{\omega}}{\partial\eta_{l}}
            d\omega
            }}
        \end{split}.
    % }
\end{equation}
Expressing the steering vector derivative with respect to $\thetaD$, results in
\begin{equation}\label{eq_vdDiff}
\frac{\partial\vd}{\partial\thetaD}=\vecnot{A}\omegaB\vd
\end{equation}
where $\vecnot{A}\omegaB$ is an $N\times{}N$ diagonal matrix with
\[
A_{ii}\omegaB=-j\omega\frac{\partial \tau_{i}}{\partial{\thetaD}}\ \  \forall{i\in\cBrace{0\hdots{}N-1}}.
\]
It is worth mentioning that \eqref{eq_vdDiff} is relevant even for arbitrary arrays (not necessarily ULA) when smooth and slowly changing radiation patterns are assumed.
In App.~\ref{apdx_clacFim} we compute the FIM terms, concluding that
\begin{equation}
    \label{eqn_FIMelements}
    \resizebox{.91\linewidth}{!}{
        \begin{split}
            &J_{11}=J_{\thetaD\thetaD}
            =
            \frac{1}{2\pi\sigma^{2}}\int_{-\omega_{s}/2}^{\omega_{s}/2}{\frac{
            \lBrace{g\vBetaH{}\vecnot{A}\omegaB\vd-g^{2}\vBetaH{}B\omegaB\vAlphaC\ePhi{-}}^{2}
            }{
            \lBrace{1-g\aHd\ePhi{-}}^{4}
            }\lBrace{\F{s}\rBrace{\omega}}^{2}d\omega}
            \\
            &J_{22}=J_{\phi\phi}
            =
            \frac{1}{2\pi\sigma^{2}}\int_{-\omega_{s}/2}^{\omega_{s}/2}{\frac{
            \lBrace{g\bHd}^{2}
            }{
            \lBrace{1-g\aHd\ePhi{-}}^{4}
            }\lBrace{\F{s}\rBrace{\omega}}^{2}d\omega}.
        \end{split}
    }
\end{equation}
where $\vecnot{B}\omegaB\triangleq\vd\vdT{}\vecnot{A}\omegaB-\vecnot{A}\omegaB\vd\vdT.$ 
% Generalizing the conventional beamformer (CB) \cite{van2004optimum}, such that the feedback weights are
% \begin{equation}\label{eq:alpha_beta_opt}
% \vAlpha_{\text{CB,opt}}=\frac{\vdC\exp\rBrace{j\phi}}{\hat{g}\norm{\vd}^2}
% \end{equation}
% where $\hat{g}$ is the channel gain estimate, both maximizes the FIM diagonal elements (via denominator minimization) and nulls it's cross-terms (see App.~\ref{apdx_clacFim}), thus significantly increases the available information.
% Assuming perfect knowledge of the target's location, while
Aiming to maximize the FIM diagonal elements via denominator (i.e., $\lBrace{1-g\aHd\ePhi{-}}$) minimization, the optimal feedback weights are 
\begin{equation}\label{eq:alpha_beta_opt}
\vAlphaC_{\text{CB,opt}}=\frac{\vdC\exp\rBrace{j\phi}}{\hat{g}\norm{\vd}^2},
\end{equation}
where $\hat{g}$ is the channel gain estimate.
This choice of weights may be interpreted as a generalized version of the conventional beamformer (CB) \cite{van2004optimum}. 
Furthermore, setting $\vBeta=\vBeta_{\text{CB,opt}}=\vAlpha_{\text{CB,opt}}$, is shown (see App.~\ref{apdx_clacFim}) to nullify the FIM cross terms, such that $J_{12}=J_{\thetaD,\phi}=J_{21}=J_{\phi\thetaD}=0.$
\par Note that setting the feedback weights as in \eqref{eq:alpha_beta_opt} requires perfect knowledge of the target's range, since $\phi$ is range dependant.
Also, the reader may notice that   assuming $\hat{g}=g$, this choice of optimal weights nullifies the denominator of  \eqref{eqn:GeneralFeedbackTransferFunction}. Thus, theoretically, the FIM becomes infinite when the transfer function \eqref{eqn:GeneralFeedbackTransferFunction} is unstable due to positive and coherent feedback between the beamformer and the target. 
In practice, though, there will be unavoidable errors, and perfect knowledge of target's location and the channel gain is usually unknown.
In Sec.~\ref{sec_Performance}, we quantify the effect of such errors and discuss its influence on the array performance. 