\personalAcknowledgementEnglish{
% I would like to thank my advisor, my parents, my friends, etc. etc.

% Add any thank-yous, acknowledgements, personal comments you wish to make here (in \texttt{personal-acks.tex}).

% Note that this acknowledgements section only gets printed in the post-exam version of the thesis (i.e. if you leave out the \texttt{beforeDefense} option to your document class in \texttt{thesis.tex}.)
First, I would like to thank my wife, Hadas, for giving me time, space and endless encouragement to finish this work inspite of all the Covid-19 realted difficulties and quarantines.
Also great gratitude is to my parents, who encouraged and helped me to set high goals and achieve them. 
\par I would also like to thank Dr. Tsvi Dvorkind for guiding me to ask the right questions without missing any details, which proved itself worthwhile with the paper being almost accepted with the first submission.
\par Special thanks goes to Prof. Israel Cohen for giving great guidance  and crucial insights from a reviewer point of view, sharing his vast knowledge and experience.
}

\personalAcknowledgementHebrew{
% אני רוצה להודות למנחה שלי, להוריי, לחבריי, וכו' וכו'.

% אפשר להוסיף עוד תודות והערות אישיות כאן.

% שים/י לב: קטע זה של תודות מודפס בפועל רק בגרסת החיבור שלאחר-הבחינה (הווה אומר רק אם הסרת את האפשרות \textenglish{\texttt{beforeDefense}} מן האפשרויות המועברות ל-\textenglish{\texttt{document class}} בקובץ \textenglish{\texttt{thesis.tex}}.)


בראש ובראשונה, תודתי נתונה לאשתי הדס על שנתנה לי את הזמן, המקום והתמיכה האינסופית לסיים את עבודה זו למרות כל הקשיים והסגרים שחווינו בעקבות התפרצות נגיף הקורונה.
הערכתי העמוקה נתונה גם להורי על שעודדו אותי לשאוף גבוה ולהשיג את מטרותי.
\par
ברצוני גם להודות לדר' צבי דבורקינד על ההדרכה הבלתי מתפשרת וההכוונה אל עבר שאילת השאלות הנכונות מבלי לפספס אף פרט, עקרונות שהוכיחו עצמם מעל ומעבר בכך שהמאמר כמעט והתקבל בהגשה הראשונה.
\par
תודה מיוחדת נתונה לפרופ' ישראל כהן על ההכוונה והליווי תוך מתן דגשים מכריעים מנקודת מבט של בוחן תוך שיתוף ידיעותיו ונסיונו הרבים.
}

